% !TEX TS-program = pdflatexmk
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{multicols}{2}
\maintitle{\\Nagarjun Chakilam}{Signal Processing Engineer}  % Your name and date of birth or subtitle

\begin{flushright}
\noindent24 Lake View Gardens, Apt 601\\ Natick, MA 01760 USA % Your address

\noindent\href{mailto:chnarjun@gmail.com}{chnarjun@gmail.com}\\% Your email address
\textsmaller{+}1 (215) 200-4755
\end{flushright}
\end{multicols}
\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after


%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

% \vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content
\begin{itemize}
\item 4+ years experience in signal processing software industry using MATLAB and Simulink.
\noindent\item 3+ years experience in testing streaming / real-time signal and audio processing algorithms applying object oriented principles.
\noindent\item Experience in developing tools to automate processes and save engineers time.
\noindent\item Experience using version control systems like Git and Perforce.
\noindent\item Strong fundamentals in digital signal processing concepts and advanced MATLAB programming.
\noindent\item Excellent time management skills and a well-versed team player.
\noindent\item Passionate about signal processing applications.
\noindent\item Hobbies include iOS app development, audio plugin development for DAWs and Raspberry Pi programming using Swift, C++ and Python respectively.

\end{itemize}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.mathworks.com}{The MathWorks, Inc.}}
{\textsc{Natick, MA}} {

\headedsubsection % Job title entry for the current employer
{Digital Signal Processing Engineer in Test \href{http://www.mathworks.com/products/dsp-system/}{\acr{\textit{DSP System Toolbox \texttrademark}}}}
{Feb '12 -- Present}
{\bodytext{
\begin{itemize}
\setlength\itemsep{1em}
\item Developed audio and signal processing algorithms using MATLAB object oriented principles as baseline for functionality testing of shipping components in DSP System Toolbox product.

\item Developed automated test suites for complex software audio and signal processing components like dynamic range control algorithms, parametric equalizer \& notch-peak filters, basic filters like low pass, high pass, differentiator filters using MATLAB and Simulink.

\item Tested optimized C code generation from several signal processing algorithms including FIR and biquad filters for ARM Cortex-A (using NE10 library) and ARM Cortex-M (using CMSIS library) processors.

\item Gathered requirements, presented software designs, developed and tested easy to use tools and saved engineers time in developing a feature and writing automated tests in MATLAB.

\item Mentored other engineers in the team to test audio related features.

\item Replaced legacy test cases with more efficient test cases without losing the code coverage and functional coverage which reduced the automated test run time by significant amount.

\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{Signal Processing Engineer Intern \href{http://www.mathworks.com/products/phased-array/}{\acr{\textit{Phased Array System Toolbox \texttrademark}}}}
{Aug '11 -- Jan '12}
{\bodytext{
\begin{itemize}
\setlength\itemsep{1em}

\item Documented and presented software designs for review.

\item Developed functions in MATLAB using radar signal processing System objects.

\item Addressed several software related bugs and enhancements.

\item Updated the product code base to a new infrastructure that makes it easier to localize the software in different languages. 
\end{itemize}
 }}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.villanova.edu}{Villanova University}}
{\textsc{ Villanova, PA }} {

\headedsubsection % Job title entry for the current employer
{Research Assistant}
{Dec '09 -- July '11}
{\bodytext{

\begin{itemize}
\setlength\itemsep{1em}
\item Developed watermarking algorithm in MATLAB to detect sonar signals in underwater acoustic channels.

\item Estimated underwater channel using least squares estimation algorithm in MATLAB.

\item Tested the watermarking algorithm in the estimated underwater channel and examined ROC curves.

\item Detected the watermarked sonar signal in the actual sea trials at the South Florida Ocean Measurement Facility. 

\end{itemize}


}}
}

%------------------------------------------------

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.villanova.edu}{Villanova University}}
{\textsc{Villanova, PA}} {

\headedsubsection % Job title entry for the current employer
{Masters in Electrical Engineering \acr{\textit{GPA: 3.97/4.0}}}
{2009 -- 2011}
{\bodytext{

Relevant coursework -- Digital Signal Processing, Statistical Signal Processing, Radar Systems and Detection \& Estimation.

}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.jntuh.ac.in}{Jawaharlal Nehru Technological University}}
{\textsc{Hyderabad, India}} {

\headedsubsection % Job title entry for the current employer
{Bachelors in Electronics \& Communications Engineering \acr{\textit{GPA: 3.92/4.0}}}
{2005 -- 2009} 
{\bodytext{

Relevant coursework -- Signals \& Systems, Digital Signal Processing, Analog Communications, Digital Communications, Linear Algebra, Matrix Theory, Probability Theory and Stochastic Processes.

}}
}

%------------------------------------------------

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Programming languages:}
{MATLAB, C, C++, Python, Swift, JAVA.}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Operating systems:}
{MAC, UNIX, WINDOWS.}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Tools:}
{Simulink, Perforce, Git, \LaTeX, Xcode.}


%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Publications} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mobasseri, B.G.; Lynch R.S.; Chakilam, N.;}
{\textbf{''Watermarking sonar waveforms using knowledge of channel coherence ''} \textit{OCEANS 2010}, pp 1-8, 20-23 Sept. 2010.}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mobasseri, B.G.; Chakilam, N.; Lynch R.S.; }
{\textbf{''Sonar Watermark Embedding and Detection: A Sea Trial Report ''} \textit{2012 SPIE Defense, Security and Sensing, Baltimore, MD.}}

\end{document}