% !TEX TS-program = pdflatexmk
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{multicols}{2}
\maintitle{\\Nagarjun Chakilam}{Audio \& DSP Quality Engineer}  % Your name and date of birth or subtitle

\begin{flushright}
\noindent24 Lake View Gardens, Apt 601\\ Natick, MA 01760 USA % Your address

\noindent\href{mailto:chnarjun@gmail.com}{chnarjun@gmail.com}\\% Your email address
\textsmaller{+}1 (215) 200-4755
\end{flushright}
\end{multicols}
\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after


%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

% \vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content
\begin{itemize}
\item 6+ years experience in signal processing software industry using MATLAB and Simulink.
\noindent\item 5+ years experience in testing streaming / real-time signal and audio processing algorithms applying object oriented principles.
\noindent\item Experience in developing tools to automate processes and save engineers time.
\noindent\item Experience using version control systems like Git and Perforce.
\noindent\item Strong fundamentals in digital signal processing concepts and advanced MATLAB programming.
\noindent\item Excellent communications skills, time management skills and a well-versed team player.
\noindent\item Passionate about signal processing applications especially in audio.
\noindent\item Hobbies include iOS app development, audio plugin development for DAWs and Raspberry Pi programming using Swift, C++ and Python respectively.

\end{itemize}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.mathworks.com}{The MathWorks, Inc.}}
{\textsc{Natick, MA}} {

\headedsubsection % Job title entry for the current employer
{Audio \& DSP Quality Engineer \href{http://www.mathworks.com/products/audio-system/}{\acr{\textit{Audio System Toolbox \texttrademark}}}}
{Feb '12 -- Present}
{\bodytext{
\begin{itemize}
\setlength\itemsep{1em}
\item Developed audio and signal processing algorithms using MATLAB object oriented principles as baseline to lock down the functionality of the shipping components.

\item Developed automated test suites for complex software audio and signal processing components using MATLAB and Simulink.

\item Took initiative in enhancing team wide processes that increased our team's productivity in multiple stages of the software development cycle. 

\item Gathered requirements, presented software designs, developed and tested easy to use tools and saved engineers time in developing a feature and writing automated tests in MATLAB.

\item Mentored several engineers and interns in the team to test audio processing algorithms and other audio related features in the product.

\item Actively participated in multiple book clubs and proactively searched for opportunities to implement what I learned.

\end{itemize}
}}

\headedsubsection % Job title entry for the current employer
{Signal Processing Engineer Intern \href{http://www.mathworks.com/products/phased-array/}{\acr{\textit{Phased Array System Toolbox \texttrademark}}}}
{Aug '11 -- Jan '12}
{\bodytext{
\begin{itemize}
\setlength\itemsep{1em}

\item Documented and presented software designs for review.

\item Developed functions for the Phased Array System Toolbox product in MATLAB.

\item Addressed several software related bugs and enhancements.

\item Updated the product code base to a new infrastructure that makes it easier to localize and internationalize the software in different languages. 
\end{itemize}
 }}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.villanova.edu}{Villanova University}}
{\textsc{ Villanova, PA }} {

\headedsubsection % Job title entry for the current employer
{Research Assistant}
{Dec '09 -- July '11}
{\bodytext{

\begin{itemize}
\setlength\itemsep{1em}
\item Developed watermarking algorithm in MATLAB to detect sonar signals in underwater acoustic channels.

\item Estimated underwater channel using least squares estimation algorithm in MATLAB.

\item Tested the watermarking algorithm in the estimated underwater channel and examined ROC curves.

\item Detected the watermarked sonar signal in the actual sea trials at the South Florida Ocean Measurement Facility. 

\end{itemize}


}}
}

%------------------------------------------------

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.villanova.edu}{Villanova University}}
{\textsc{Villanova, PA}} {

\headedsubsection % Job title entry for the current employer
{Masters in Electrical Engineering \acr{\textit{GPA: 3.97/4.0}}}
{2009 -- 2011}
{\bodytext{

}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.cvr.ac.in}{CVR College of Engineering}}
{\textsc{Hyderabad, India}} {

\headedsubsection % Job title entry for the current employer
{Bachelors in Electronics \& Communications Engineering \acr{\textit{GPA: 3.92/4.0}}}
{2005 -- 2009} 
{\bodytext{


}}
}

%------------------------------------------------

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Programming languages:}
{MATLAB, C, C++, Python, Swift, JAVA.}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Operating systems:}
{MAC, UNIX, WINDOWS.}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Tools:}
{Simulink, Perforce, Git, \LaTeX, Xcode.}


%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Publications} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mobasseri, B.G.; Lynch R.S.; Chakilam, N.;}
{\textbf{''Watermarking sonar waveforms using knowledge of channel coherence ''} \textit{OCEANS 2010}, pp 1-8, 20-23 Sept. 2010.}

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Mobasseri, B.G.; Chakilam, N.; Lynch R.S.; }
{\textbf{''Sonar Watermark Embedding and Detection: A Sea Trial Report ''} \textit{2012 SPIE Defense, Security and Sensing, Baltimore, MD.}}

\end{document}